---
title: "Freby corperation"
author: "George.B"
date: "2022-12-17"
output:
  pdf_document: default
  html_document: default
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(dplyr)
library(janitor)
library(skimr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(colorspace)
library(here)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
library(readr)
Companies_Stock_History <- read_csv("C:/Users/pc/Desktop/my project raw file/Stock-History/Companies_Stock_History.csv")
View(Companies_Stock_History)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
Companies_Stock_History$date <- mdy(Companies_Stock_History$Date)
Companies_Stock_History$Month <- format(as.Date(Companies_Stock_History$date), "%m")
Companies_Stock_History$Day <- format(as.Date(Companies_Stock_History$date), "%d")
Companies_Stock_History$Year <- format(as.Date(Companies_Stock_History$date), "%Y")
```


# Summary
#### Project Problem.
* Which of the top 10 US companies has the Highest unit of share traded in th pass five years.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
Companies_yearly_stock <- Companies_Stock_History %>% 
  group_by(Year, Company) %>% 
  drop_na() %>% 
  summarise(max_Open=max(Open),max_High=max(High),max_Low=max(Low),max_Close=max(Close),max_Volume=max(Volume))
print(Companies_yearly_stock)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = Companies_yearly_stock)+
  geom_col(mapping = aes(x=Company, y=max_Volume, fill=Company))+
  theme(axis.text.x = element_text(angle = 45))+
  theme(axis.text.y = element_text(angle = 40))+
  facet_wrap(~Year)+
  labs(title = "Maximum: Yearly Volume", 
       subtitle = "Highest Unit of Shares Traded on a Yearly Bases")
```

* The chart showcases the highest amount of volume traded the a single day in a year.
* Apple, Amazon and Nvidia has the highest amount of unit of share traded in the stock market. 



```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = Companies_yearly_stock)+
  geom_col(mapping = aes(x=Company, y=max_Open, fill=Company))+
  theme(axis.text.x = element_text(angle = 45))+
  theme(axis.text.y = element_text(angle = 40))+
  facet_wrap(~Year)+
  labs(title = "Maximum: Open trades", 
       subtitle = "Highest Unit of Shares Traded on a Yearly Bases")
```

* The chart showcases the highest amount of Open trades the a single day in a year.
* Netflix and Tesla has the highest amount of Open trades in the stock market.


```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = Companies_yearly_stock)+
  geom_col(mapping = aes(x=Company, y=max_High, fill=Company))+
  theme(axis.text.x = element_text(angle = 45))+
  theme(axis.text.y = element_text(angle = 40))+
  facet_wrap(~Year)+
  labs(title = "Maximum: High trades", 
       subtitle = "Highest Unit of Shares Traded on a Yearly Bases")
```

* The chart shows the amount of high trades a single unit of share cost in the market the a single day in a year.
* Netflix and Tesla still has the highest amount of high trades in the stock market.



```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = Companies_yearly_stock)+
  geom_col(mapping = aes(x=Company, y=max_Close, fill=Company))+
  theme(axis.text.x = element_text(angle = 45))+
  theme(axis.text.y = element_text(angle = 40))+
  facet_wrap(~Year)+
  labs(title = "Maximum: Close trades", 
       subtitle = "Highest Unit of Shares Traded on a Yearly Bases")
```

* The chart showcases the highest amount of Close trades a single unit of share was sold at, at the end of the working day in a year.
* Netflix and Tesla has the highest amount of Close trades in the stock market.



```{r message=FALSE, warning=FALSE, include=FALSE}
library(readr)
company_yearly_trades <- read_csv("company_yearly_trades.csv")
View(company_yearly_trades)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
company_yearly_trades2 <- company_yearly_trades %>% 
  group_by(Company,total_volume_traded_yearly) %>% 
  summarise(total_volume_traded_yearly=max(total_volume_traded_yearly))
print(company_yearly_trades2)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = company_yearly_trades2)+
  geom_col(mapping=aes(x=Company, y=total_volume_traded_yearly),color="red")+
  labs(title = "Total Volume", subtitle = "Total Units of Shares Traded from 2017 to 2022")
```

* The chart shows the total amount of Volume traded from 2017 to 2022 the the companies.
* Apple has the highest amount of unit of share traded in the market with an estimate of $150 billion shares traded in the 6 years, then followed by Amazon with an estimated share of over $109 billion shares traded from 2017  to 2022.



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
company_yearly_trades3 <- company_yearly_trades %>% 
  group_by(Company,total_volume_traded_yearly_dollar) %>% 
  summarise(total_volume_traded_yearly_dollar=max(total_volume_traded_yearly_dollar))
print(company_yearly_trades3)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = company_yearly_trades3)+
  geom_col(mapping = aes(x=Company, y=total_volume_traded_yearly_dollar), color="green")+
  labs(title = "Volume in Dollars", subtitle = "Total Units of Shares Traded from 2017 to 2022")
```

* The chart shows the total amount of Volume traded in Dollars from 2017 to 2022 the the companies.
* Tesla, Apple and Amazon has the highest amount of volume traded in Dollars which is as follows:-
* Tesla $15,400,000,000,000 from 2017 to 2022
* Apple $12,400,000,000,000 from 2017 to 2022
* Amazon $12,200,000,000,000 from 2017 to 2022.
* The amount in Dollar was gotten by multiplying Volume with Adj Close.